Models

### 2024-04-24 analysis/05_model_metrics.Rmd
fix p.values not updated

model_output <- bind_rows(metric_model_table, indv_mod_table) %>%
  left_join(pval_df) %>%
  select(-significant, -tval)

@@

Summaries of study slopes
```{r}
#First - how many studies had a significant trend for each metric? 
model_output %>% 
  filter(!is.na(study_id)) %>%
  filter(term == "year_scaled", p.value < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S", "FRic", "FEve", "FDiv")) %>% 
  mutate(positive = ifelse(estimate > 0, TRUE, FALSE)) %>%
  group_by(metric, positive) %>% 
  summarise(n_study_id = n_distinct(study_id)) %>%
  pivot_wider(names_from = "metric", values_from = "n_study_id")

#And which studies were they?
model_output %>% 
  filter(!is.na(study_id)) %>%
  filter(term == "year_scaled", p.value < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S", "FRic", "FEve", "FDiv")) %>% 
  select(study_id, metric) %>%
  distinct()

#Which were significant for multiple metrics?
model_output %>% 
  filter(!is.na(study_id)) %>%
  filter(term == "year_scaled", p.value < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  group_by(study_id) %>%
  filter(n() > 1) %>%
  select(study_id, metric)
```

>>>>

model_output <- bind_rows(metric_model_table, indv_mod_table) %>%
  select(-p.value) %>% 
  left_join(pval_df) %>%
  select(-significant, -tval)

@@

Summaries of study slopes
```{r}
#First - how many studies had a significant trend for each metric? 
model_output %>% 
  filter(!is.na(study_id)) %>%
  filter(term == "year_scaled", p.adjust < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S", "FRic", "FEve", "FDiv")) %>% 
  mutate(positive = ifelse(estimate > 0, TRUE, FALSE)) %>%
  group_by(metric, positive) %>% 
  summarise(n_study_id = n_distinct(study_id)) %>%
  pivot_wider(names_from = "metric", values_from = "n_study_id")

#And which studies were they?
model_output %>% 
  filter(!is.na(study_id)) %>%
  filter(term == "year_scaled", p.adjust < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S", "FRic", "FEve", "FDiv")) %>% 
  select(study_id, metric) %>%
  distinct()

#Which were significant for multiple metrics?
model_output %>% 
  filter(!is.na(study_id)) %>%
  filter(term == "year_scaled", p.adjust < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  group_by(study_id) %>%
  filter(n() > 1) %>%
  select(study_id, metric)
```
